Concurrent Programming with Harmony

### 2020-07-20 book/paper.tex
Latest

\section*{Exercises}
\begin{problems}
\item The \texttt{produce} method in \autoref{fig:boundedbuffer} cannot be used
from interrupt handlers for two reasons: (1) it is not interrupt-safe, and (2)
it may block for a long time if the buffer is full.  Yet, it would be useful if,
say, a keyboard interrupt handler could place an event on a shared queue.  Implement
a new method \texttt{iproduce}(\textit{item}) that is interrupt-safe and does not
block.  Instead, it should return \texttt{False} if the buffer is full and \texttt{True}
if the item was successfully enqueued.
\end{problems}

>>>>

\section*{Exercises}
\begin{problems}
\item The \texttt{produce} method in \autoref{fig:boundedbuffer} cannot be used
in interrupt handlers for two reasons: (1) it is not interrupt-safe, and (2)
it may block for a long time if the buffer is full.  Yet, it would be useful if,
say, a keyboard interrupt handler could place an event on a shared queue.  Implement
a new method \texttt{iproduce}(\textit{item}) that is interrupt-safe and does not
block.  Instead, it should return \texttt{False} if the buffer is full and \texttt{True}
if the item was successfully enqueued.
\end{problems}
